---
title: "Vignette Title"
author: "Oscar Ramírez-Alán"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You have installed resumeR on your R system, version 3.4.4 or later "https://cran.r-project.org/". Works better in Rstudio "https://www.rstudio.com"

What should you do?

1. Activate the resumeR package:

```{r}
library(resumeR)
```

You could requiere "e1071";  "car" and "carData" package

- Never uses retina figures.
- Never uses a smaller size windows for your plot.

2. load you data

```{r}
set.seed(12345)
data<-rnorm(100)
```

3. get a descriptive summary plot and table

```{r, fig.width=7, fig.height=6}
resume(rnorm(100))
```

4. get a complete summary table, histogram and boxplot of your distribution data.

```{r, fig.width=7, fig.height=5}
resume2data(data)
```


5. For you data.frame get a summarie table

```{r}
data(CO2)
resumendf(conc ~Type, data=CO2)
```


## Figures

If you are interested in exploring the distribution of your data using a histogram, use "plothist". 

```{r, fig.width=7, fig.height=5, fig.cap = "Histogram"}
set.seed(12345)
data<-rnorm(100)
plothist(data)
```





##Installing the package

> 
library(devtools)
> 
devtools::install_github("osoramirez/Sinax4")

